\textit{Supplemental materials for}: How is experience transformed into memory?

### 2018-09-04 paper/supplemental_materials.tex
updated supp mat fig captions related to topic models

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/parameter_search}
\caption{\small \textbf{Optimizing video model parameters.} Matrices representing the correlation value between hand-annotated memory performance and mean squared error between video model and recall model. Best fitting model was 100 topics, 50 video window size and 10 recall window size}
\label{fig:paramsearch}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Impact of individual features on topic modeling analysis.} \textbf{A.} Contribution of each feature to model structure. Bars represent the correlation of a video model trained in the absence of a given feature to the model trained on all features. \textbf{B.} Contribution of each feature to video model/recall model relationship. The leftmost bar represents the across-participants mean correlation between the video model and recall models trained on all features. Subsequent bars represent the same relationship between video and recall models trained in the absence of a given feature. Error bars are the standard error of the mean across participants. \textbf{C.}  Individual feature trajectory similarity matrix. The first row/column is the topic trajectory the full video model. Each subsequent row/column is that of a single feature. Shading corresponds to the value of the correlation coefficient (Pearson's $r$) .}
\label{fig:feature-importance}
\end{figure}

@@

\textbf{JRM STOPPED HERE.  NOTE: STILL NEED TO LOOK AT FIG CAPTIONS TOO...}

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/parameter_search}
\caption{\small \textbf{Optimizing topic model parameters.}  We performed a grid search over movie sliding window length ($\omega \in \{5, 10, 25, 50, 100 \}$), recall sliding window length ($\rho \in \{5, 10, 25, 50, 100 \}$, and number of topics ($K \in \{5, 10, 25, 50, 100 \}$.  The reported correlations are between per-subject video-recall trajectory correlations and per-subject hand-annotated memory performance ratings.}
\label{fig:paramsearch}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\textwidth]{figs/feature_value}
\caption{\small \textbf{Feature importance analysis.} \textbf{A.} Contributions of each feature type to the structure of the video trajectory. The bar heights reflect the correlation between the video trajectory computed using all features with a video trajectory computed using all features except the indicated feature.  (Lower bars reflect features that contribute more substantially to the video trajectory's shape.) \textbf{B.} Which features are preserved during recall?  The bar heights reflect the (average) across-participant correlations between the video and recall trajectories.  Error bars denote 95\% confidence intervals.  \textbf{C.} Feature correlation matrix.  Each entry displays the correlation between video topic trajectories created using only the indicated (row/column) features.}
\label{fig:feature-importance}
\end{figure}

@@

\textbf{JRM STOPPED HERE.}
